%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% Modified by Alvin Jude
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper]{scrartcl}

%\reversemarginpar % Move the margin to the left of the page
\pagenumbering{gobble} % No need for page numbers

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage{hyperref} % Required for adding links       and customizing them
\usepackage{multicol}
\usepackage{enumitem}
\setlist{nolistsep,leftmargin=*}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage
[
        a4paper,% other options: a3paper, a5paper, etc
        left=1.5cm,
        right=1.5cm,
        top=1.8cm,
        bottom=1.8cm,
        % use vmargin=2cm to make vertical margins equal to 2cm.
        % us  hmargin=3cm to make horizontal margins equal to 3cm.
        % use margin=3cm to make all margins  equal to 3cm.
]
{geometry}

\setlength{\multicolsep}{0pt}
\setlength\parindent{0pt}


%% Setup themes based on color. Some of my favorite: MidnightBlue, Teal, RoyalNavy, RubineRed
\colorlet{ThemeColor}{Maroon}

\hypersetup{colorlinks, breaklinks, urlcolor=ThemeColor, linkcolor=ThemeColor} % Set link colors
\newlength{\datebox}\settowidth{\datebox}{2014 to present} % Set the width of the date box in each block
\newcommand{\Columize}[2]{\noindent \parbox{2cm}{{#1}} {#2} } % Add some white space after each new entry
\newcommand{\Description}[1]{\hangindent=0em\hangafter=0\noindent\small{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here
\newcommand{\Redvline}[0]{\vspace{0em}\noindent{\color{ThemeColor}\rule{18cm}{0.4pt}}\vspace{-0.5em}}
\newcommand{\MyName}[1]{\noindent{\textsc{\LARGE{\color{ThemeColor}#1}}}} % Font color of your name at the top
%% Generally #1: margin left contents, #2: Dates #3 Title
\newcommand{\NewBlock}[3]{
    #1\ \ $\cdotp$\ \ #2\ \ $\cdotp$\ \ #3}
%% BADHACK here. Because otherwise the margin text immediately after this will be off
\newcommand{\BlockTitle}[1]{\textsc{\vspace{0.15em}}\noindent{\spacedlowsmallcaps{#1}}\vspace{1em}}
%\newcommand{\Publication}[5]{{#1}\newline{#2}\newline{#3} ({#5})\newline\href{http://dx.doi.org/#4}{http://dx.doi.org/{#4}}}
\newcommand{\Publication}[5]{\textbf{{#1}}\newline\hspace{1cm}{#2}\newline{#3}}
%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------


%\vspace{-0.3em}


\MyName{Alvin Jude} % Your name

\href{mailto:alvin@dartarrow.net}{alvin@dartarrow.net} % Email address
\hspace*{\fill}
\href{http://dartarrow.net/research}{http://dartarrow.net/research} % Personal website
\hspace*{\fill}
\href{tel:+1 (254) 413 1023}{+1 (254) 413 1023}

\Redvline
\vspace{1em} % Extra white space between the personal information section and goal

%\BlockTitle{About} % About heading, could be used for a quotation or short profile or "goals"

\Description{I am a Human-Computer Interaction researcher currently working in the domain of Digital Representation \& Interaction. My current research interests include spatial audio and mixed realities, ethics in AI, crowdsourcing, and human-centred machine learning.
I have previously worked and published works on content discovery and recommendations, similarity, and mid-air gestural interaction \& pointing devices. I've also performed introspective research within the company to assess and improve internal systems and processes.
I've previously held positions in system administration and software development. I seek to combine my deep technical background with my constantly improving understanding of human factors to make technology more human.
}

\Redvline
%----------------------------------------------------------------------------------------
%       EDUCATION
%----------------------------------------------------------------------------------------

\BlockTitle{Education}

\Description{Masters of Psychology $\cdotp$\ Arden University $\cdotp$\ 2018--2021 (expected)}

\Description{Masters of Computer Science $\cdotp$\ Baylor University $\cdotp$\ 2012--2014

\textsc{Thesis:} Giving the Users a Hand: Towards Touchless Hand Gestures for the Desktop
}

\Description{Bachelor of Computer Science $\cdotp$\ Coventry University $\cdotp$\ 2002--2005

\textsc{Thesis:} Remote PC Manipulation via PDA over Bluetooth
}
%------------------------------------------------

\Redvline
%----------------------------------------------------------------------------------------
%       PUBLICATIONS
%----------------------------------------------------------------------------------------

\BlockTitle{Publications}

\Description{\Publication{Finding Similar Movies: Dataset, Tools, and Methods}
{Hongkun Leng, Caleb De La Cruz Paulino, Momina Haider, Rui Lu, Zhehui Zhou, Ole Mengshoel, Per-Erik Brodin, Julien Forgeat, Alvin Jude}
{HCI-Europe 2018. International Conference in Central Europe on Human Computer Interaction}
{DOI unknown}
{2018}}

\Description{\Publication{I Don't Need To See That: Seeking, Avoiding, and Attempting to Control Video Content}
{Jennifer Lee, Alvin Jude, Meral Shirazipour, Julien Forgeat}
{CHI '18. Extended Abstracts on Human Factors in Computing Systems}
{DOI unknown}
{2018}}

\Description{\Publication{Content-Based Top-N Recommendations With Perceived Similarity}
{Charlie Wang, Arpita Agrawal, Xiaojun Li, Tanima Makkad, Ejaz Veljee, Ole Mengshoel, and Alvin Jude}
{SMC '17. IEEE International Conference on Systems, Man, and Cybernetics}
{DOI unknown}
{2017}}

\Description{\Publication{Bimanual Word Gesture Keyboards for Mid-air Gestures}
{Garrett Benoit, G. Michael Poor, Alvin Jude}
{CHI '17. Extended Abstracts on Human Factors in Computing Systems}
{DOI unknown}
{2017}}

\Description{\Publication{Incremental Learning for Matrix Factorization in Recommender Systems}
{Tong Yu, Ole Mengshoel, Alvin Jude, Eugen Feller, Julien Forgeat, Nimish Radia}
{Big Data 2016. IEEE International Conference on Big Data}
{unknown}
{2016}}

\Description{\Publication{Improving Gestural Interaction With Augmented Cursors}
{Ashley Dover, G. Michael Poor, Darren Guinness, and Alvin Jude}
{SUI '16. ACM Symposium on Spatial User Interaction}
{10.1145/2983310.2985765}
{2016}}

\Description{\Publication{Grasp, Grab or Pinch? Identifying User Preference for In-Air Gestural Manipulation}
{Alvin Jude, G. Michael Poor, and Darren Guinness}
{SUI '16. ACM Symposium on Spatial User Interaction}
{10.1145/2983310.2989209}
{2016}}

\Description{\Publication{Reporting and Visualizing Fitts’ Law: Dataset, Tools and Methodologies}
{Alvin Jude, Darren Guinness, and G. Michael Poor}
{CHI '16. Extended Abstracts on Human Factors in Computing Systems}
{10.1145/2851581.2892364}
{2016}}

\Description{\Publication{Evaluating Item-Item Similarity Algorithms for Movies}
{Lucas Colucci, Prachi Doshi, Kun-Lin Lee, Jiajie Liang, Yin Lin, Ishan Vashishtha, Jia Zhang, and Alvin Jude}
{CHI '16. Extended Abstracts on Human Factors in Computing Systems}
{10.1145/2851581.2892362}
{2016}}

\Description{\Publication{Models for Rested Touchless Gestural Interaction}
{Darren Guinness, Alvin Jude, G. Michael Poor, and Ashley Dover}
{SUI '15. ACM Symposium on Spatial User Interaction}
{10.1145/2788940.2788948}
{2015}}

\Description{\Publication{Modeling Mid-air Gestures With Spherical Coordinates}
{Darren Guinness, Andrew Seung, Ashley Dover, G. Michael Poor, and Alvin Jude}
{SUI '15. ACM Symposium on Spatial User Interaction}
{10.1145/2788940.2794356}
{2015}}

\Description{\Publication{Personal Space: User Defined Gesture Space for GUI Interaction.}
{Alvin Jude, G. Michael Poor, and Darren Guinness}
{CHI '14. Extended Abstracts on Human Factors in Computing Systems}
{10.1145/2559206.2581242}
{2014}}

\Description{\Publication{An Evaluation of Touchless Hand Gestural Interaction for Pointing Tasks with Preferred and Non-preferred Hands.}
{Alvin Jude, G. Michael Poor, and Darren Guinness}
{NordiCHI '14. Proceedings of the 8th Nordic Conference on Human-Computer Interaction}
{10.1145/2639189.2641207}
{2014}}

\Description{\Publication{Evaluating Multimodal Interaction with Gestures and Speech for Point and Select Tasks}
{Alvin Jude, G. Michael Poor, and Darren Guinness}
{NordiCHI '14. Proceedings of the 8th Nordic Conference on Human-Computer Interaction}
{10.1145/2639189.2670267}
{2014}}

\Description{\Publication{Gestures with Speech for Hand-Impaired Persons}
{Darren Guinness, G. Michael Poor, and Alvin Jude}
{ASSETS '14. 16th International ACM SIGACCESS Conference on Computers and Accessibility}
{10.1145/2661334.2661398}
{2014}}

\Redvline
%----------------------------------------------------------------------------------------
%	Writings
%----------------------------------------------------------------------------------------

\BlockTitle{Other Publications}

\Description{\Publication{User study for media metadata extraction}
{Alvin Jude, Ji-Yeon Yang, Jennifer Lee, Julien Forgeat, Meral Shirazipour}
{Ericsson Research Blog: \footnotesize{https://www.ericsson.com/research-blog/user-study-media-metadata-extraction/}}
{}
{2018}}

\Description{\Publication{Learning things we never knew we never knew}
{Alvin Jude}
{Ericsson Research Blog: \footnotesize{https://www.ericsson.com/research-blog/learning-things-never-knew-never-knew/}}
{}
{2018}}

\Description{\Publication{The Future of Sports Visualization}
{Alvin Jude}
{Ericsson Research Blog: \footnotesize{https://www.ericsson.com/research-blog/future-sports-visualization/}}
{}
{2018}}

\Description{\Publication{Patents}
{6 patents filed in the area of recommender systems, and network integration thereof.}
{1 patent in improving remote AR collaboration, 1 in improving usability of secure file sharing.}
{}
{}}

\Description{\Publication{Internal Publication}
{Ericsson Tech Insider: Recommender Systems}
{Contributed to Ericsson CTO Trends 2018 -- Internet of Skills}
{}
{}}

\Redvline
%----------------------------------------------------------------------------------------
% Service
%----------------------------------------------------------------------------------------

\BlockTitle{Service}
\Description{
\begin{itemize}
    \item Conference section chair, HCI-Europe
    \item Reviewer, ACM TOCHI, ACM CHI, IJHCI, ACM SUI, IEEE SMC
    \item Ericsson Research Young Advisory Board
    \item Speaker, FOSS.my. Topic: Passive monitoring with Collectd
    \item Ericsson patent reviewer
\end{itemize}
}

\newpage
\Redvline
%----------------------------------------------------------------------------------------
%	Technical SKILLS
%----------------------------------------------------------------------------------------

\BlockTitle{Technical Skills}
\newlength{\techskills} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\techskills}{Intermediate} % Length equals the length of "Intermediate"

%\Description{\parbox{\techskills}{\textsc{Basic}}: R $\cdotp$\ \textsc{Matlab} $\cdotp$\ C\# $\cdotp$\ Tomcat $\cdotp$\ HBase $\cdotp$ JQuery $\cdotp$ \textsc{Css3} $\cdotp$ HAProxy  $\cdotp$ Heartbeat $\cdotp$ DRBD
%\parbox{\techskills}{\textsc{Intermediate}}: Python $\cdotp$\ \LaTeX \ $\cdotp$\ C $\cdotp$\ PostgreSQL $\cdotp$\ Nmap $\cdotp$\ Git $\cdotp$\ Hibernate $\cdotp$\ Objective-C $\cdotp$\ Memcached
%\parbox{\techskills}{\textsc{Advanced}}: NGinX $\cdotp$\ Puppet $\cdotp$\ Nagios $\cdotp$\ Collectd $\cdotp$\ PHP5 $\cdotp$\ MySQL $\cdotp$\ Java $\cdotp$\ Symfony $\cdotp$\ OpenVZ
\Description{
\begin{center}
\begin{minipage}[t]{0.33333\textwidth}
\raggedright
\textsc{Basic}
\begin{itemize}
    \item NodeJS
    \item CSS3
    \item HTML5
    \item Ember.js
    \item Cassandra
    \item Nagios
    \item Qualitative Research
    \item SPSS
\end{itemize}
\end{minipage}%
\begin{minipage}[t]{0.33333\textwidth}
\textsc{Intermediate}
\raggedright
\begin{itemize}
    \item Python
    \item Machine Learning
    \item JQuery
    \item SQL
    \item R
    \item Matlab
    \item Java
    \item Personalisation
    %\item Interactive Information Retrieval
\end{itemize}
\end{minipage}%
\begin{minipage}[t]{0.33333\textwidth}
\textsc{Advanced}
\raggedright
\begin{itemize}
    \item PHP
    \item Recommender Systems
    \item User Experience (UX)
    \item Usability Testing
    \item Experimental Design
    \item Hypothesis Testing
    \item Gestural Interaction
    \item Quantitative Research
\end{itemize}
\end{minipage}
\end{center}
}

\begin{comment}
\Description{\parbox{\techskills}{\textsc{Basic}}: NodeJS $\cdotp$\ CSS3 $\cdotp$\ HTML5 $\cdotp$\ Ember.js $\cdotp$\ Cassandra $\cdotp$\ Nagios $\cdotp$\ Qualitative Research $\cdotp$\ Machine Learning

\parbox{\techskills}{\textsc{Intermediate}}: Python $\cdotp$\ PHP5 $\cdotp$\ \LaTeX \ $\cdotp$\ JQuery $\cdotp$\ MySQL $\cdotp$\ R $\cdotp$\ Matlab $\cdotp$\ Java $\cdotp$\ Recommender Systems $\cdotp$\ Personalisation $\cdotp$\ Interactive Information Retrieval

\parbox{\techskills}{\textsc{Advanced}}: User Experience (UX) $\cdotp$\ Usability Testing $\cdotp$\ Experimental Design $\cdotp$\ Hypothesis Testing $\cdotp$\ Gestural Interaction $\cdotp$\ Quantitative Research
}
\end{comment}
\Redvline

\BlockTitle{Other Skills}
\newlength{\nontechskills} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\nontechskills}{Entrepreneurship} % Length equals the length of "Entrepreneurship"

\Description{\parbox{\nontechskills}{\textsc{Communication}}: Former Malaysian Public Speaking Champion

\parbox{\nontechskills}{\textsc{Entrepreneurship}}: Baylor NewVenture 2014: Top-5 Finalist \& 3rd place Elevator Pitch

\parbox{\nontechskills}{\textsc{Martial Arts}}: Taekwondo, Karate, Aikido, MMA, Krav Maga
}

% Suggest a new page here
%\Redvline
%\newpage
%\MyName{Alvin Jude} % Your name Again.

\Redvline
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\BlockTitle{Work Experience}

\NewBlock{Ericsson}{2014--present}{Senior Researcher}

\Description{Improved discovery of similar items by 38\%, saw research from conceptualisation and prototyping through to productization.
Led usability testing of new content discovery methods with a European partner. Mentored over 20 students from Carnegie Mellon University as part of practicum project. Recruited and led 10 HCI interns.
Performed self-driven research for patent portfolio. Defined \textit{Interaction} research agenda for current research area.
%\\Reference: Nimish Radia\ \ $\cdotp$\ \ \href{mailto:nimish.radia@ericsson.com}{nimish.radia@ericsson.com}
}

\NewBlock{Baylor University}{2013--2014}{Research Assistant}

\Description{Setup new HCI lab. Mentored juniors, established engineering procedures and infrastructure. Performed research in hand-gestural interaction and explored research options with other next-generation input devices.
Overhauled software used for teaching database.
Assisted in developing lab curriculum for teaching operating systems.
%Reference: G. Michael Poor\ \ $\cdotp$\ \href{mailto:michael\_poor@baylor.edu}{michael\_poor@baylor.edu} \\
%Reference: Greg Speegle\ \ $\cdotp$\ \ \href{mailto:greg\_speegle@baylor.edu}{greg\_speegle@baylor.edu}
}

%------------------------------------------------

\NewBlock{Self Employed}{2010--2012}{Technical Consultant}

\Description{Served as an independent consultant for various project and companies including the following:}
\begin{enumerate}
\item[] \Description{iOS Development, \textsc{Agile Perspectives --- Malaysia}, 2011--2012
\newline
Performed R\&D for use of Apple products in financial services. Built and deployed app for one international insurance corporation. Built app for a consumer-facing startup dealing in retail. Role included requirements gathering, feasibility studies, business case development, and technical consultation. }

\item[] \Description{System Administration, \textsc{CouchSurfing.org}, 2010--2011
\newline
%Daily operations: monitoring, security, optimization, deployment, etc.
Deployed a cluster of static content servers with NGinX to reduce the load off the dynamic servers, which resulted in higher reliability or website as a whole. Tools of the trade included Puppet, Zabbix, HAProxy. }
\end{enumerate}

%------------------------------------------------
\NewBlock{Aflexi (now OnApp CDN)}{2009--2010}{System Engineer}

\Description{Responsibilities were more DevOps involving backend development and system administration. Built a custom monitoring infrastructure from the ground up (traditionally done with Nagios) on a specialized Collectd infrastructure used to feed PowerDNS for DNS-based CDN routing. Tools of the trade included Puppet, Zabbix, Nagios, RRD.
%\\Reference: Whei Wong\ \ $\cdotp$\ \ \href{mailto:whei.wong@onapp.com}{whei.wong@onapp.com}
}

%------------------------------------------------

\NewBlock{iMocha Consulting}{2007--2010}{Software Engineer}

\Description{Initially hired as a Junior Java Developer, but quickly tasked to build and run a LAMP team of up to 8 people, dealing mostly with financial institutions. Responsibilities leading development work, mentoring programmers, system administrators, system analysts, and interns, as well as requirements gathering from clients.
%\\Reference: Koh Kok Wei\ \ $\cdotp$\ \ \href{mailto:kokwei@imocha.com.my}{kokwei@imocha.com.my}
}
%------------------------------------------------

\NewBlock{Sony Manufacturing}{2005--2007}{Engineer}

\Description{Developed a tool used to trace products which helped cut down traceability time from 2 working days to about 4 hours. Tools of the trade included MFC, VB.NET, PHP, Postgres, GTK.}
%------------------------------------------------
\Redvline
\end{document}
